### 2013-11-05 article2013.Rmd
regression modelling. Just before going into multinomial regression

<link href="http://markuskainu.fi/material/css/article.css" rel="stylesheet" type="text/css" title="compact"></link>
<link href='http://fonts.googleapis.com/css?family=Alegreya+SC|Dosis:400,200' rel='stylesheet' type='text/css'>

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="latex",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.pdf)

@@

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.pdf)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.pdf)

@@

```{rattribArticleMultilevel1,results='asis', eval=FALSE}
source("~/workspace/lits/attrib/attrib_year2013/code/multi_logit.R")
library(texreg)
texreg(list(soc.0,
       soc.1,
       soc.2,
       soc.3,
       soc.4),
       use.package=FALSE,
       include.pvalues=TRUE,
       ci.test=NULL,

          caption="Logistic multilevel random intercept model for social blame type of explanation.", caption.above=TRUE, doctype = FALSE,
        custom.coef.names=c("Intercept",
                             "Transfer dependency (Not dependent)",
                             "Education (No education)",
                             "Perceived income (Low)",
                             "Perceived change in income compared to four years ago (Has worsened)",
                             "Expected change in income over next four years (Will worsen)",
                             "Effect of financial crisis (Suffered great or fair amount)",
                             "gini coefficient",
                             "GDP change 2007-2010",
                             "Voice And Accountability (WB)"),
        custom.model.names=c("empty","Model SB1","Model SB2",
                             "Model SB3","Model SB4"))

```{rattribArticleMultilevel2, results='asis', eval=FALSE}

texreg(list(ind.0,
          ind.1,
          ind.2,
          ind.3,
          ind.4),
       use.packages=FALSE,
       include.pvalues=TRUE,
       ci.test=NULL,
       caption="Logistic multilevel random intercept model for individual blame type of explanation.", 
       caption.above=TRUE, 
        doctype = FALSE,
                custom.coef.names=c("Intercept",
                             "Transfer dependency (Not dependent)",
                             "Education (No education)",
                             "Perceived income (Low)",
                             "Perceived change in income compared to four years ago (Has worsened)",
                             "Expected change in income over next four years (Will worsen)",
                             "Effect of financial crisis (Suffered great or fair amount)",
                             "gini coefficient",
                             "GDP change 2007-2010",
                             "Voice And Accountability (WB)"),
        custom.model.names=c("empty","Model IB1","Model IB2",
                             "Model IB3","Model IB4"))
```

>>>>

<link href="http://markuskainu.fi/material/css/rmarkdown.css" rel="stylesheet" type="text/css" title="compact"></link>

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),
              type="html",
              comment=FALSE, 
              include.rownames=FALSE,
             caption.placement="top")

@@

![Change in total GDP in 2007 - 2010 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gdp.png)

@@

![Gini coefficient and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_gini.png)

@@

![World Bank's Voice and Accountability index in 2011 and support for social (left) and individual (right) blame types of attributions for poverty](figure/scatter_wbgi.png)

@@

### 2013-11-05 index.Rmd
regression modelling. Just before going into multinomial regression

@@

-------------------
html-ouput                                                    source code
-------------------                                           ---------
[loading, cleaning and summarizing](loadClean.html)           [source](loadClean.Rmd)
-------------------

@@

-------------------
html-ouput                                                source code
-----------------------                                   ---------
[Descriptive analysis](descriptive_analysis.html)         [source](descriptive_analysis.Rmd)

@@

-------------------
html-ouput                                                source code
-----------------------                                   ---------
[Regression analysis](code/multilevel_models.html)        [source](code/multilevel_models.Rmd)

>>>>

`log of changes`

date      comment
--------  -------------------
20131103  Regression modelling in process. Final models will be published on Tuesday afternoon

@@

-------------------
html-ouput                                          source code
------------                                        --------------
[loading, cleaning and summarizing](loadClean.html) [source](loadClean.Rmd)
-------------------

@@

-------------------
html-ouput                                        source code
------------                                      --------------
[Descriptive analysis](descriptive_analysis.html) [source](descriptive_analysis.Rmd)

[Spatial visualization](mapPlots.html)            [source]((mapPlots.Rmd))

@@

-------------------
html-ouput                                                source code
------------                                              --------------
[Regression analysis](regressionModelling.html)           [source](regressionModelling.Rmd)

### 2013-11-05 loadClean.Rmd
regression modelling. Just before going into multinomial regression

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=TRUE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

lits2$income <- factor(lits2$income2, 
                       levels=c("Low",
                                "High"))

@@

lits2$crise <- factor(lits2$crise, levels=c("Little or not at all",
                                            "Great or fair amount"))
summary(lits2$crise)
```

@@

library(ggplot2)
ggplot(datQogSum, aes(x=year,y=value,color=cname)) + 
  geom_point(size=4) +
  geom_text(data = datQogSum,
            aes(x=year,y=value,
                color=cname,
                label=cname),
            size=3.5) +
  facet_wrap(~indicator, scales="free") +
  theme(legend.position="none")

@@

datQogSum.w$group_general[datQogSum.w$cname %in% c('France','Germany',
                                                   'Great Britain','Italy','Sweden')] <- 'Western Europe';
datQogSum.w$group_general[datQogSum.w$cname %in% c('Czech Republic','Estonia',
                                                   'Hungary','Bulgaria',
                                                   'Latvia','Lithuania','Poland',
                                                   'Slovakia','Slovenia','Romania')] <- 'CEE'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Belarus',
                                                   'Georgia','Kazakhstan',
                                                   'Kyrgyzstan','Moldova',
                                                   'Tajikistan','Ukraine',
                                                   'Uzbekistan','Russia')] <- 'CIS'

datQogSum.w$group_general <- factor(datQogSum.w$group_general)
summary(datQogSum.w$group_general)

df.qog <- datQogSum.w
# underschores into dots for latex...
#names <- names(df.qog)
#library(stringr)
#names <- str_replace_all(names, "_",".")
#names(df.qog) <- names
library(gdata)
names(df.qog)[1] <- "cntry"
```

>>>>

```{roptsattrib, echo=FALSE}
opts_chunk$set(echo=TRUE,eval=TRUE, cache=FALSE,message=FALSE,warning=FALSE,fig.width=12,fig.height=12)
```

@@

lits2$income2 <- factor(lits2$income2, 
                       levels=c("Low",
                                "High"))

@@

lits2$crise <- factor(lits2$crise, levels=c("Great or fair amount",
                                            "Little or not at all"))
summary(lits2$crise)
```

@@

# library(ggplot2)
# ggplot(datQogSum, aes(x=year,y=value,color=cname)) + 
#   geom_point(size=4) +
#   geom_text(data = datQogSum,
#             aes(x=year,y=value,
#                 color=cname,
#                 label=cname),
#             size=3.5) +
#   facet_wrap(~indicator, scales="free") +
#   theme(legend.position="none")

@@

datQogSum.w$group_general[datQogSum.w$cname %in% c('France','Germany',
                                                   'Great Britain','Italy','Sweden')] <- 'Western Europe'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Czech Republic','Estonia',
                                                   'Hungary','Bulgaria',
                                                   'Latvia','Lithuania','Poland',
                                                   'Slovakia','Slovenia','Romania')] <- 'CEE'
datQogSum.w$group_general[datQogSum.w$cname %in% c('Armenia','Azerbaijan','Belarus',
                                                   'Georgia','Kazakhstan',
                                                   'Kyrgyzstan','Moldova',
                                                   'Tajikistan','Ukraine',
                                                   'Uzbekistan','Russia')] <- 'CIS'

datQogSum.w$group_general <- factor(datQogSum.w$group_general)

df.qog <- datQogSum.w
# underschores into dots for latex...
#names <- names(df.qog)
#library(stringr)
#names <- str_replace_all(names, "_",".")
#names(df.qog) <- names
names(df.qog)[1] <- "cntry"
```
